Software Citation Principles

### 2016-04-18 sc-principles/software-citation-principles.tex
adding citation limits subsection in 5 to address https://github.com/force11/force11-scwg/issues/122

>>>>

\subsection{Citations limits}

This set of software citation principles, if followed, will cause the number of software citations
in scholarly products to increase, thus causing the number of overall citations to increase.
Some scholarly products that are or were once printed on paper, such as journal articles,
may have strict
limits on the number of citations they permit, partially imposed to reduce production costs.
Such limits are counter to our recommendation.
\textit{Citation limits, if absolutely required, should accommodate rather than stifle software citation} (and resource citation, and data citation.)
